%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
  {PhD candidate} 
  {OUTSCALE}
  {Paris, France} % Location
  {2015 - 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
      \item {Addressed the problem of \textbf{ML-based resource allocation} (CPU, memory, disk) on Outscale's industrial, Infrastructure as a Service cloud.}
      \item{To identify unaddressed technological barriers in cloud resource allocation, programmed a workload monitoring agent compliant with privacy constraints and coordinated testing and deployment. This work laid the foundation to a user-facing monitoring service.}
      \item{\textbf{Characterized the workload} and compared it with previous studies from the scientific literature. Found that short virtual machine (VM) run time and HW/SW heterogeneity reduced the potential benefit of VM migrations to balance the workload.}
      \item{Built a \textbf{workload classification model} which uses text mining to outperform models from the literature: F1=.9 vs F1=.74.} 
      \item{\textbf{Evaluated the sensitivity} of a ML-based resource allocation algorithm with respect to prediction error.}
      \item{Communicated on research results and animated round tables on Big Data at Outscale's yearly event for clients and partners.}
      \item{Anonymized the collected data set so that it could be published to strengthen ties between the company and public research institutions.}
      \end{cvitems}
    }



%%---------------------------------------------------------
%  \cventry
%  {Bull, High Performance Computing} % Organization
%  {Software Development Intern} % Job title
%  {Grenoble, France} % Location
%    {2012 (2 months)} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%      \item {Wrote a script to automate the documentation of a network card based on specifications extracted from a database.}
%      \end{cvitems}
%    }
%---------------------------------------------------------
  \cventry
  {Network/System Consultant Intern} % Job title
  {CNS Communications} % Organization
  {Lyon, France} % Location
    {2013 (5 months)} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Performed the audit and the migration of the LAN/WAN infrastructure of several branch offices of a publicly listed company.}
      \item {Troubleshot network failures for public administrations (hospitals and universities).}
     % \item {Migrated virtualized ToIP, DNS, DHCP \& AD services on a VMware infrastructure.}  
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
